---
title: "Sample maps"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: 'Version: `r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are some sample maps made in [Lingtypology](https://ropensci.org/blog/2017/05/16/lingtypology/) for R with the Daghestanian villages and languages dataset.

See the `sample_maps.rmd` file in the [repository](https://github.com/sverhees/master_villages) for the code used to draw these maps.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# packages

library(tidyverse) # data manipulation
library(lingtypology) # drawing maps

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# load data

vill <- read_tsv("data/villages.csv") # dataframe with all villages, coordinates and languages
meta <- read_tsv("data/meta.csv") # dataframe with language metadata and color schemes

# data preparation

vill <- vill[complete.cases(vill$lat),] # remove villages without coordinates

meta_core <- meta %>% # remove idioms not (yet) recognized as distinct
  filter(core == "yes")

vill_meta <- merge(vill, meta_core, by = "lang") # merge villages with metadata

```

## Map with all villages by language

The color scheme on this map more or less reflects genetic affiliation in the East Caucasian family, based on the ordering in [this family tree by Schulze (2009)](https://en.wikipedia.org/wiki/Northeast_Caucasian_languages#/media/File:Northeast_Caucasian_Splits.png). Unrelated languages are shades of grey and white. Hover over a dot to see the language spoken in a particular village.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.height= 7.5}

# re-order the elements in the legend (by default they are in alphabetical order)

vill_meta$lang <- factor(vill_meta$lang, levels =c(
  "Dargwa", "Lak", "Bats", "Ingush", "Chechen", "Khinalug", "Archi", "Tsakhur", "Rutul", "Kryz", "Budukh", "Udi", "Lezgian", "Agul", "Tabasaran", "Avar", "Andi", "Botlikh", "Godoberi", "Chamalal", "Bagvalal", "Tindi", "Karata", "Akhvakh", "Tsez", "Hinuq", "Bezhta", "Hunzib", "Khwarshi", "Nogai", "Kumyk", "Azerbaijani", "Armenian", "Tat", "Georgian"))

# draw map

map.feature(lang.gltc(vill_meta$glottocode),
            latitude = vill_meta$lat,
            longitude = vill_meta$lon,
            features = vill_meta$lang,
            color = vill_meta$lang_color,
            label = vill_meta$lang,
            zoom.control = T,
            popup = vill_meta$village,
            tile = c("Esri.WorldTopoMap"))

```


## Map with all villages by genealogical group

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.height= 7.5}

vill_meta$aff <- factor(vill_meta$aff, levels =c("Dargwa", "Lak", "Nakh", "Khinalug", "Lezgic", "Avar", "Andic", "Tsezic", "Kipchak", "Oghuz", "Armenic", "Iranian", "Georgic"))

map.feature(lang.gltc(vill_meta$glottocode),
            latitude = vill_meta$lat,
            longitude = vill_meta$lon,
            features = vill_meta$aff,
            width = 8,
            label = vill_meta$lang,
            color = vill_meta$aff_color,
            zoom.control = T,
            popup = vill_meta$village,
            tile = c("Esri.WorldTopoMap"))

```

## Map with all villages by language + general datapoints

A lighter version of the previous colorscheme is also available. The idea is that you can use the lighter shades for all villages, and the brighter colors for villages that you have data for. Below is an example with general datapoints (i.e. one point for each traditionally recognized language and coordinates from the [Glottolog](https://glottolog.org/) database).

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.height= 7.5}

meta_core$emphasis <- "emphasis"

map.feature(lang.gltc(vill_meta$glottocode),
            latitude = vill_meta$lat,
            longitude = vill_meta$lon,
            features = vill_meta$lang,
            color = vill_meta$lang_color_pale,
            label = vill_meta$lang,
            zoom.control = T,
            popup = vill_meta$village,
            tile = c("Esri.WorldTopoMap")) %>%
    map.feature(lang.gltc(meta_core$glottocode),
            latitude = meta_core$gen_lat,
            longitude = meta_core$gen_lon,
            features = meta_core$lang,
            legend = FALSE,
            stroke.features = meta_core$emphasis,
            stroke.color = "black",
            stroke.legend = F,
            width = 3, stroke.radius = 5,
            label = meta_core$lang,
            color = meta_core$lang_color,
            zoom.control = T,
            pipe.data = .)
```

## Map with only general datapoints

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.height= 7.5}

meta_core$lang <- factor(meta_core$lang, levels =c(
  "Dargwa", "Lak", "Bats", "Ingush", "Chechen", "Khinalug", "Archi", "Tsakhur", "Rutul", "Kryz", "Budukh", "Udi", "Lezgian", "Agul", "Tabasaran", "Avar", "Andi", "Botlikh", "Godoberi", "Chamalal", "Bagvalal", "Tindi", "Karata", "Akhvakh", "Tsez", "Hinuq", "Bezhta", "Hunzib", "Khwarshi", "Nogai", "Kumyk", "Azerbaijani", "Armenian", "Tat", "Georgian"))

map.feature(lang.gltc(meta_core$glottocode),
            latitude = meta_core$gen_lat,
            longitude = meta_core$gen_lon,
            features = meta_core$lang,
            label = meta_core$lang,
            color = meta_core$lang_color,
            zoom.control = T)

```

## Altitude of datapoints

The altitude for each datapoint was retrieved automatically from Google, as were the coordinates for each village. These coordinates are not always precisely in the centre of the village, and as a result, the altitude data contains some inaccuracies. The highest village in this dataset, for example, is the village Asha (Tsumadinsky district), while we know that the highest village in Daghestan is actually Kurush (Dokuzparinsky district).

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 9.5, fig.height= 7.5}

# round off elevation to two decimals

vill_meta <- vill_meta %>%
  mutate(round = round(elevation, 2))

map.feature(lang.gltc(vill_meta$glottocode),
            latitude = vill_meta$lat,
            longitude = vill_meta$lon,
            features = vill_meta$round,
            title = "Altitude",
            popup = paste(vill_meta$village, "<br>", "Meters above sea-level:", vill_meta$elevation))

```




